Milk intake and stroke mortality in the Japan Collaborative Cohort Study - a Bayesian survival analysis

### 2020-07-14 Paperfolder/Paperfolder.Rmd
updated almost abstract done

  To further examine the relationship between milk intake and stroke mortality among the Japanese population. We used 

>>>>

  To further examine the relationship between milk intake and stroke mortality among the Japanese population. We used data from the Japan Collaborative Cohort Study to estimate the posterior acceleration factors as well as the hazard ratios comparing individuals with different milk intake frequencies against those who never consumed milk at the study baseline. These estimations were computed through a series of Bayesian survival models that employed a Markov Chain Monte Carlo simulation process. 100000 posterior samples for each individual were generated separately through four independent chains after model convergency were confirmed. Posterior probabilites that daily male consumers of milk 

### 2020-07-14 Paperfolder/Paperfolder.tex
updated almost abstract done

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{To further examine the relationship between milk intake and
stroke mortality among the Japanese population. We used}

>>>>

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{To further examine the relationship between milk intake and
stroke mortality among the Japanese population. We used data from the
Japan Collaborative Cohort Study to estimate the posterior acceleration
factors as well as the hazard ratios comparing individuals with
different milk intake frequencies against those who never consumed milk
at the study baseline. These estimations were computed through a series
of Bayesian survival models that employed a Markov Chain Monte Carlo
simulation process. 100000 posterior samples for each individual were
generated separately through four independent chains after model
convergency were confirmed. Posterior probabilites that daily male
consumers of milk}
